The response theory for the system under a non-equilibrium driving

### 2013-06-12 writedown/linear.response/paper.tex
new title and add abs

\title{Linear response theory for core set identification}
\author{Han Wang}
\author{Carsten Hartmann}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
\author{Christof Sch\"utte}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
\affiliation{Zuse Institute Berlin (ZIB), Germany}
% \affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}

@@

\begin{abstract}
  % In this draft, we are trying to study the core set based Markov
  % State Model (MSM) under non-equilirbium conditions.
\end{abstract}

>>>>

% \title{Linear response theory for core set identification}
\title{The response theory for the system under a non-equilibrium driving}
\author{Han Wang}
\author{Carsten Hartmann}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
\author{Christof Sch\"utte}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
\affiliation{Zuse Institute Berlin (ZIB), Germany}
% \affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}

@@

\begin{abstract}
  In this talk, we firstly review the traditional linear response
  theory, and then generalize it to the system under a non-equilibrium
  driving. We calculate not only the linear response term, but also
  the higher order terms with respect to the perturbation to the
  reference dynamics. The response theory is applied to investigate
  the dynamics of core set that plays a central role in the Markov
  State Model (MSM). The advantages and limitations are discussed from
  the numerical tests.
  % In this draft, we are trying to study the core set based Markov
  % State Model (MSM) under non-equilirbium conditions.
\end{abstract}
